---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# penumbra

<!-- badges: start -->
<!-- badges: end -->

This is an R package based on Neal McKee's [penumbra color palette](https://github.com/nealmckee/penumbra/).

From the original:

>Penumbra is a mathematically balanced colour scheme constructed in a
perceptually uniform colour space with base colours inspired by the shades of
colour occuring in nature due to the light of the sun and the sky. It cleanly
separates the perceptual properties of colours while optimally utilising the
available colour space of typical displays.

> ...

> The accent colour palettes also lend themselves to encoding quantitative 
information in data visualisations.

## Installation

You can install the development version of penumbra like so:

``` r
remotes::install_github("hughjonesd/penumbra")
```

## Example

```{r example}
library(penumbra)
## basic example code
palette(penumbra::color_pal(n = 7, contrast = "contrast+"))
plot(1:7, pch = 19, cex = 5, col = 1:7)
```
